\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\graphicspath{ {figures/} }
\usepackage{array}
\usepackage{float}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{amsfonts}
\newcommand{\C}{{\mathbb C}}
\newcommand{\E}{{\mathbb E}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\Prr}{{\mathbb P}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\D}{{\mathbb D}}
\newcommand{\Z}{{\mathbb Z}}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.18}
\usepackage{booktabs}
\usepackage{array}
\usepackage{colortbl}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{note}{Note}[section]

% Redefine the format for figure captions
\captionsetup[figure]{
    labelfont={bf},   % Make the label bold (e.g., "Figure 1")
    labelsep=colon,   % Set the separator after the label (optional, default is a colon)
}


\title{Collection of Results}
\author{Prof. Serhiy Kozak \& James Zhang}
\date{\today}

\begin{document}

\maketitle

% \tableofcontents

% \newpage

All results in this document pertain to the SCS dataset. All 
window sizes are $120$ months. The out-of-sample start date is January $1$, $2005$. Recall that we study a three-dimensional tensor $\mathcal{R}$ of excess returns ie. returns minus the 
risk-free rate, where
\begin{align}
    \mathcal{R}_{t, l, i} \ \ \ t = 1, \ldots, T, l = 1, \ldots, L, i = 1, \ldots, N,
\end{align}
Residuals are defined as differences between returns and the factor model's implied returns. For the tensor model, this is 
\begin{align}
    \epsilon_{t, l, i} = \mathcal{R}_{t, l, i} - \sum_{k=1}^K \lambda_k F_{t, k} W_{l, k} B_{i, k}
\end{align}

NOTE: there is a slight issue with our statistics related to our PCA estimator. We're doing it in a PooledPCA fashion, which we eliminated 
from the multiperiod section of our results, so this would be inconsistent.

\begin{enumerate}
    \item In-sample evaluations
    \begin{itemize}
        \item Reconstruction error as a function of $K$ and $L$ for unconstrained, orthogonal tensor models 
        and also as a function of rank for PCA model.
        \begin{align}
            \epsilon_{rc} = 1 - \frac{\left\lVert \mathcal{R} - \mathcal{R}_{rc}\right\lVert^2_F}{\left\lVert \mathcal{R}\right\rVert^2_F}
        \end{align}
        \item Excess alpha. First we define pricing errors for a single asset across time as 
        \begin{align}
            \alpha_{l, i} = \frac{1}{T}\sum_{t=1}^T \epsilon_{t, l, i}
        \end{align}
        Then it follows that excess alpha for all assets and lags is 
        \begin{align}
            \text{XS-}\alpha = \frac{1}{NL}\sqrt{\sum_{i=1}^N \sum_{l=1}^L \alpha^2_{l, i}}
        \end{align}
        \item Similarly, for a single asset, the unexplained variance over time is 
        \begin{align}
            \sigma^2_{\epsilon, l, i} = \frac{1}{T} \sum_{t=1}^T \epsilon^2_{t, l, i} - \alpha^2_{l, i}
        \end{align}
        It follows that the normalized averaged unexplained variance is 
        \begin{align}
            \sigma_{\epsilon} = \sqrt{\frac{1}{NL} \sum_{i=1}^N \sum_{l=1}^L \sigma^2_{\epsilon, l, i}} \Bigg\slash \sqrt{\frac{1}{NL} \sum_{i=1}^N \sum_{l=1}^L \left[\text{Var}_t(\mathcal{R})\right]_{l, i}}
        \end{align}
        \item Pricing errors
        \item Term structure of fitted mean returns for the models?
    \end{itemize}
    \item Out-of-sample evals
    \begin{itemize}
        \item Reconstruction errors
        \item Excess alphas
        \item Normalized unepxlained variances
    \end{itemize}
    \item Multiperiod results - unconstrained TFM, Naive, Hor1, Orthogonal, PCA, and RP-PCA (note to self: make the axis the same for all plots in this 2x3)
    \item Tensor model visualizations and economic content
\end{enumerate}

\end{document}
